---
title: "week8"
output: html_document
date: "2023-04-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Review of week 6

```{r}
dropboxlink = "https://www.dropbox.com/s/6vhwbxnzc0fz3is/90-107%E5%AD%B8%E5%B9%B4%E5%BA%A6%E5%A4%A7%E5%AD%B8%E9%83%A8%E8%AA%B2%E7%A8%8B%E8%B3%87%E6%96%99.csv?dl=1"
courses <- readr::read_csv(dropboxlink)
```

```{r}
ntpuCourses <- list()
```

## Courses on Wednesday

  * About pulling out subsample based on some criterion (filter)

```{r}
# split data frame based on a column 
courses |> split(courses$學年) -> ntpuCourses$dataSplit$byYear

# focus on only 107 school year
targetCourses <- ntpuCourses$dataSplit$byYear$`107` 
View(targetCourses)
## What courses are available on Wednesday?
### 1. filtered based on logical expressions
pick <- grepl("週三", targetCourses$上課時間教室)
head(pick)
targetCourses[pick, ] -> ntpuCourses$wedCourseIn107
ntpuCourses$wedCourseIn107 |> 
  dplyr::glimpse()

### 2. filtered based on positions
pos <- grep("週三", targetCourses$上課時間教室)
head(pos)
targetCourses[pos, ] |> 
  dplyr::glimpse()

### 3. use dplyr::filter
targetCourses |>
  dplyr::filter(grepl("週三", targetCourses$上課時間教室)) |> 
  dplyr::glimpse()
```

-   logical expression is to return a vector of **logicals** that tells us which element meet the condition.

```{r}
timePlace <- 
  c("每週一3~4　商1F16", "每週四6~8　社113", "每週五3~4　文4F05_L", 
"每週三7~8　文2F02", "隔週教室資1F-10、每週五3~4　資1F-10", 
"每週一3~4　文4F08", "每週五7~8　", "每週一5~6　社112", 
"每週三5~6　", "每週二5~6　文2F01")

# logical expression: equivalent
timePlace == "每週二5~6　文2F01"
timePlace == "週三"
# logical expression: contain
grepl("週三", timePlace)
```

# For each

## Each 開課系所 

-   How many courses were offered?

```{r}
targetCourses$開課系所 |> class()
```

```{r}
targetCourses$開課系所 |> table() |> sort()
```

  * table result is actually an integer atomic vector with element names. 


## Each 學院

```{r}
data.frame(
  department = c("")
)
```

# Factor

```{r}
bloodTypes <- c("AB", "AB", "A", "B", "A", "A", "B", "O", "O", "AB")
```

```{r}
class(bloodTypes)
```

```{r}
bloodTypes <- factor(bloodTypes)
class(bloodTypes)
```

When R saves factor vector, the storage type becomes integer with a level table as extra mapping information
```{r}
levels(bloodTypes)
```

```{r}
print(bloodTypes)
```

```{r}
bloodTypes |> as.integer()
```


```{r}
levels(bloodTypes)
```

```{r}
bloodTypes2 <- factor(bloodTypes, levels = c("A", "B", "AB", "O"))
levels(bloodTypes2)
table(bloodTypes2)
```

```{r}
table(bloodTypes)
```


```{r}
targetCourses$開課系所 |> factor() ->
  targetCourses$開課系所

class(targetCourses$開課系所)
```

```{r}
levels(targetCourses$開課系所)
```

# Ordered factor

```{r}
household_income <- c("low income", "low income", "middle income", "low income", "high income", "middle income", "high income", "high income", "middle income", "middle income")

class(household_income)
```

```{r}
household_income[[10]] > "low income"
"middle income" > "low income"
"m" > "l"
```

```{r}
"a" > "b"
"aa" > "ab"
```

```{r}
household_income <- factor(household_income, ordered = T, levels = c("low income", "middle income", "high income"))
```


```{r}
class(household_income)
```

```{r}
household_income[[10]] == "high income"
```


```{r}
levels(household_income) <- c("low income", "high income", "high income")
```

```{r}
household_income
```
```{r}
sample(
  c("statistics", "finance", "economics", "sociology"), 
  20, 
  replace = T) -> departments
```

```{r}
departments <- factor(departments)
departments
```
```{r}
school <- departments
levels(school)
levels(school) <- c("social science", "business", "social science", "statistics")

school
```


