---
title: "week 5"
output: html_document
date: "2023-03-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Create a google form to take attendance

# Time zone

## Create a google form to take attendance

## Import data from google sheets

> how to import data from google sheets in R

### ChatGPT answer

To import data from Google Sheets in R, you can use the "googlesheets4" package. Here are the steps:

1. Install the "googlesheets4" package using the following command:

```
install.packages("googlesheets4")
```

2. Load the package using the following command:

```
library(googlesheets4)
```

3. Authenticate with Google Sheets by running the following command:

```
gs4_auth()
```

4. Once you are authenticated, you can import data from a Google Sheet by running the following command:

```
my_sheet <- gs4_get("https://docs.google.com/spreadsheets/d/1abcdefg/edit#gid=123456789")
```

Replace the URL with the URL of the Google Sheet that you want to import. The "gid" parameter in the URL specifies the sheet ID. If you want to import a specific sheet, make sure to include the correct sheet ID in the URL.

5. Once the data is imported, you can use standard R functions to manipulate and analyze the data.

Note that you will need to have permissions to access the Google Sheet in order to import the data.

### Code

```{r}
library(googlesheets4)
```

```{r}
gs4_auth()
```

```{r}
mySheet <- gs4_get("https://docs.google.com/spreadsheets/d/187LRBCzcHCetea9ZsCnWOUFDdXCfVIZx3R2vvPsmh4I/edit#gid=91650247")
```


# List

Two types of vectors

  * Atomic vectors: all element values are of the same type.
  
```{r}
atomicVec0 <- c(2, 23.1, 22, 100, -100, Inf, -Inf, NA)
atomicVec1 <- c(T, T, F, FALSE, TRUE, FALSE, NA)
atomicVec2 <- c("Martin", "Janet", "Jim")
```

  * list: no restriction on element values, and is created using `list(...)`
  
```{r}
# three element values
list0 <- list(2, "Martin", FALSE)
list1 <- list(
  2, 
   c("Martin", "Janet", "Jim"),
  FALSE
)
# vector of length 3
list2 <- list(
  list("Mary", 32, TRUE), 
  list("Martin", 40, FALSE),
  list("Janet", 20, TRUE)
)
```
 
    * list allows user to nest informations. 

## Element names

```{r}
list3 = list(name="Mary", age=32, isMarried=TRUE)
```


## data frame 

is a special list.

  * element name becomes column name.
  
  * element values are all atomic vector of the same length

Consider `list2`

```{r}
list2 <- list(
  list("Mary", 32, TRUE), 
  list("Martin", 40, FALSE),
  list("Janet", 20, TRUE)
)
class(list2)
```

  
```{r}
dataFrame2 <- list(
  name = c("Mary", "Martin", "Janet"),
  age = c(32, 40, 20),
  isMarried = c(T, F, T) 
)

class(dataFrame2)

dataframe2 = data.frame(dataFrame2)

class(dataframe2)
```

data frame is a list that has been parsed.


```{r}
# it is the same as
dataFrame2 <- data.frame(list(
  name = c("Mary", "Martin", "Janet"),
  age = c(32, 40, 20),
  isMarried = c(T, F, T) 
))
# or 
dataFrame2 <- data.frame(
  name = c("Mary", "Martin", "Janet"),
  age = c(32, 40, 20),
  isMarried = c(T, F, T) 
)
```

  * Anything your learn about list also works on data frame




